Highly Available Transactions: Virtues and Limitations

### 2013-03-31 writeup/conclusion.tex
new conclusion

\section{Conclusion}
The current state of database software offers uncomfortable and unnecessary
choices between availability and transactional semantics.
In this paper we expose a broad design space of Highly Available Transactional 
Systems (HATs), which can offer the key benefits of
highly available distributed systems---partition tolerance and low-latency 
writes---while also providing a family of transactional isolation 
levels and replica semantics that have been widely used in practice. 
In taxonomizing this design space, we show that many transactional 
guarantees are achievable with high availability, while a few, 
like preventing Lost Update and Write Skew, are not.

There has been some debate in the database community regarding the importance
of availability in modern databases; there is also concern about the utility of
relaxed isolation.  Our analysis and experiments in Sections~\ref{sec:motivation} 
and~\ref{sec:evaluation} convince us that the availability goals of the NoSQL
movement will remain a critical aspect of many important systems going forward, and 
that the isolation levels available via HATs can have significant practical impact
in delivering useful transactional semantics to application developers.

Much of the prior research in distributed transactions has focused on prototyping 
individual points in the design space, with a focus on providing serializability
at the expense of availability.  Our goal in this paper has been to take a broader view. 
We taxonomize the joint design space of replica consistency and transactional isolation,
and identify what is possible and impossible to achieve semantically via HATs.  From
a research perspective, this offers a long-overdue connection between storage 
semantics studied in the database and distributed systems communities.
With this understanding in hand, the next challenge is to return to issues of 
performance and systems architecture within the HATs design space.  Based on our 
understanding of what is desired in the field and what is possible to achieve, we 
believe this is an area of great opportunity in the coming years.

>>>>

\section{Conclusion}
The current state of database software offers uncomfortable and
unnecessary choices between availability and transactional semantics.
We show, however, through analysis and experiments, that the
availability goals of the NoSQL movement will remain a critical aspect
of many important systems going forward. Thus, we expose a broad
design space of Highly Available Transactional Systems (HATs), which
can offer the key benefits of highly available distributed
systems---partition tolerance and low-latency writes---while also
providing a family of transactional isolation levels and replica
semantics that have been widely used in practice.  In taxonomizing
this design space, we show that many transactional guarantees are
achievable with high availability, while a few, like preventing Lost
Update and Write Skew, are not. From a research perspective, this
offers a long-overdue connection between storage semantics studied in
the database and distributed systems communities.

With the above understanding in hand, the next challenge is to return to
issues of performance and systems architecture within the HATs design
space.  Based on our understanding of what is desired in the field and
what is possible to achieve, we believe this is an area of great
opportunity in the coming years.

%% In this paper we expose a broad design space of Highly Available Transactional 
%% Systems (HATs), which can offer the key benefits of
%% highly available distributed systems---partition tolerance and low-latency 
%% writes---while also providing a family of transactional isolation 
%% levels and replica semantics that have been widely used in practice. 
%% In taxonomizing this design space, we show that many transactional 
%% guarantees are achievable with high availability, while a few, 
%% like preventing Lost Update and Write Skew, are not.

%% There has been some debate in the database community regarding the importance
%% of availability in modern databases; there is also concern about the utility of
%% relaxed isolation.  Our analysis and experiments in Sections~\ref{sec:motivation} 
%% and~\ref{sec:evaluation} convince us that the availability goals of the NoSQL
%% movement will remain a critical aspect of many important systems going forward, and 
%% that the isolation levels available via HATs can have significant practical impact
%% in delivering useful transactional semantics to application developers.

%% Much of the prior research in distributed transactions has focused on prototyping 
%% individual points in the design space, with a focus on providing serializability
%% at the expense of availability.  Our goal in this paper has been to take a broader view. 
%% We taxonomize the joint design space of replica consistency and transactional isolation,
%% and identify what is possible and impossible to achieve semantically via HATs.  From
%% a research perspective, this offers a long-overdue connection between storage 
%% semantics studied in the database and distributed systems communities.
%% With this understanding in hand, the next challenge is to return to issues of 
%% performance and systems architecture within the HATs design space.  Based on our 
%% understanding of what is desired in the field and what is possible to achieve, we 
%% believe this is an area of great opportunity in the coming years.
